%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{multicol}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}

\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\setlength{\multicolsep}{0pt plus 0pt}
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemNoColon}[2]{
  \item\small{
    \textbf{#1}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemNew}[1]{
	\item{
		{#1}
	}

	
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeNewItem}[1]{\resumeItemNew{#1}\vspace{-7pt}}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-5pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
 \textbf{\href{https://www.linkedin.com/in/daniyal-selani-745022174/}{\Large Daniyal Selani}} & Email: \href{mailto:daniyal.9538@gmail.com}{daniyal.9538@gmail.com}\\
{}& {{Phone: +31685681702}}\\ & \href{https://github.com/daniyal9538}{github.com/daniyal9538} \\
\vspace{-10.5mm}
\end{tabular*}

%-----------EXPERIENCE-----------------


\section{Experience}
  \resumeSubHeadingListStart
\resumeSubheading
      {ING}{September 2022 - Present}
      {Data Scientists}{Amsterdam, Netherlands}
      \resumeItemListStart
        \resumeItem  {Churn Prediction}
          {Designed a churn prediction system for evaluating the likelihood of customers leaving ING services.}
      
	      \resumeItemListEnd

 \resumeSubheading
      {Philips}{January 2022 - July 2022}
      {AI for Language Research Intern}{Eindhoven, Netherlands}
      \resumeItemListStart
        \resumeItem  {Log Data Modeling for Maintenance}
          {Developed deep learning models for log data generated by medical devices for down stream predictive maintenance and diagnostic tasks.}
        \resumeItem  {Philips Intern Committee Board Member}
          {Facilitated social and career events for the intern community at Philips.}
	      \resumeItemListEnd
\resumeSubheading
      {VU Amsterdam}{November 2021 - July 2022}
      {Research Assistant}{Amsterdam, Netherlands}
      \resumeItemListStart
        \resumeItem  {AI for epitope prediction}
          {Developed data pipelines to feed deep learning model for the task of epitope prediction.}
     
	      \resumeItemListEnd
 \resumeSubheading
      {OneByte}{September 2019 - December 2021}
      {Data Scientist}{Remote Work}
      \resumeItemListStart
        \resumeItem  {\href{https://eonhealth.com/wp-content/uploads/2020/10/Eon_White_Paper_CL_Pulmonary_Nodules_081620.pdf}{Data Extraction and Classification System}}
          {Created, evaluated, and maintained data extraction and classification models for identifying actionable findings and organ-specific abnormalities in patient screening and monitoring systems at Eon Healthcare.}

        \resumeItem  {Procedure Mapper}
          {Developed a model to map medical procedure names from different hospitals to a standardized lexicon.}
 \resumeItem{Model Assessments}
          {Implemented custom pipeline for model assessment by domain experts. The pipeline also included monitoring system that provides an overview of expert feedback and progress.}
 %\resumeItem{Script Monitoring System}
          %{Monitoring system for model assessing pipeline.}
 \resumeItem{Tagmoo (Cattle ID System)}
          {Developed a system for identifying individual cattle using computer vision and biometric data from their muzzle prints.}

      \resumeItemListEnd

    \resumeSubheading
      {Paitoo}{February 2019 - September 2019}
      {Machine Learning Engineer}{Lahore, Pakistan}
      \resumeItemListStart
        \resumeItem{Recommendation Engine}
          {Developed a recommendation engine for food centered social media app (Paitoo).}
	\resumeItem{Classification System}
          {Developed a hierarchical image classification model to automatically classify dishes in Paitoo database.}
%Hierarchical image classification model to automatically classify dishes in the Paitoo database.}
\resumeItem{Ranking Optimization}
          {Developed, tested and maintained a system to identify and rank trending restaurants and items within the app.}
%Ranking optimizations to maintain and update "Trending items" list within the app. }
        \resumeItem{Data Analysis}
          {Provided data driven insights about user behavior. }
%Data analysis on user generated data for tracking revenue and business growth.}
      \resumeItemListEnd

    \resumeSubheading
      {DataLog - CodeNConsult}{May 2018 - September 2018 }
      {Computer Engineer Internee}{Karachi, Pakistan}
 


    

  \resumeSubHeadingListEnd

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Masters in Artificial Intelligence}{August 2020 -- July 2022}
{VU Amsterdam}{Amsterdam, Netherlands}
  \resumeItemListStart
\resumeItem{Research Assistant} {Exploring deep learning strategies for effective knowledge transfer in epitope prediction.}
  \resumeItemListEnd
\resumeSubheading
{Bachelors of Science in Computer Engineering}{August 2014 -- June 2019}
{Middle East Technical University}{North Cyprus, Turkey}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects and Publications}
  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://github.com/daniyal9538/coactivation_AE_AD}{Auto-Encoder Knowledge Extraction for Anomaly Detection Task}}
      {Knowledge extraction from auto-encoders on anomaly detection tasks using co-activation graphs (ACM K-CAP conference 2021).}

\resumeSubItem{\href{https://exploringaiblog.wordpress.com/2019/09/20/implementing-hierarchical-categories-with-an-ensemble-classifier-to-overcome-dataset-limitations/}{Boolean Logic Ensemble Method}}
      {Hierarchical categories with a novel boolean logic ensemble classifier to overcome dataset limitations.}
\resumeSubItem{\href{https://github.com/daniyal9538/CID}{Graduation Project (CID)}}
      {Modular self-driving system for use in virtual environments.}
    %\resumeSubItem{\href{https://exploringaiblog.wordpress.com/}{Exploring AI Blog}}
      %{Personal blog in which I write either tutorials explaining basic concepts of  machine learning, an analysis on any related topics, or my thoughts on  anything related to technology.}
    
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
     \item{
    	\textbf{Proficient with}{: Python  -  SkLearn - OpenCV -  Pandas - TensorFlow - Keras - Git - Pytorch - Elastic Search - Linux - SQL}
    }
    
    \item{
    	\textbf{Have Knowledge of}{: C++ - IoT Technology - C\# - Azure - AWS  - Raspberry Pi}
    	
    }
 \resumeSubHeadingListEnd


%-----------EDUCATION-----------------

%\vspace{2in}

%----------Courses---------
\section{Selected Coursework}
\resumeSubHeadingListStart
\begin{multicols}{2}

	\resumeNewItem{Machine Learning}
	\resumeNewItem{Artificial Intelligence}
	\resumeNewItem{Experimental Design and Data Analysis}		
	\resumeNewItem{Knowledge Representation}
	\resumeNewItem{Socially Intelligent Robotics }
	\resumeNewItem{Evolutionary Computing}
\resumeNewItem{BioInformatics}
	\resumeNewItem{Multi-Agent Systems}
	\resumeNewItem{Data Mining}
	\resumeNewItem{NLP Technologies}
	\resumeNewItem{Machine Learning and Reasoning for Healthcare}
	
	
\end{multicols}
\resumeSubHeadingListEnd
%



%-------------------------------------------
\end{document}